---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis
pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html
walks through it in detail. This R Markdown report the example from the chapter.
Try it out in both interactive and non-interactive modes, either by running the
code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above.

```{r, eval = FALSE}
install.packages(c("biglm", "dplyr", "ggplot2", "readr", "targets", "tidyr"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

```{r}
library(targets)
```

Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_config_set(store = "/mnt/parscratch/users/bi1ahd/pre_process_xStressorsStabBEFW_targets/")
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
dir_fun <- "~/xStressorsStabBEFW/"
source(paste0(dir_fun, "R/network_metrics.R"))
source(paste0(dir_fun, "R/string_replacements.R"))
source(paste0(dir_fun, "R/stability_decomposition.R"))
source(paste0(dir_fun, "R/model_helpers.R"))
source(paste0(dir_fun, "R/sem_helpers.R"))
compute_metabolic_loss <- function(Z = NULL, tlvl = NULL, ax = .88, bx = -0.25) {
  M = Z ^ (tlvl - 1)
  x = ax*M^(bx)
  x[tlvl == 1] <- 0 
  x
}
```

# Targets

Our first target borrows the `airquality` dataset built into base R.

## Sim with metabolic death 

```{targets raw_sim}
list(
  tar_target(sim_dir, "/mnt/parscratch/users/bi1ahd/sim/simCSh/"),
  tar_target(var_param_sim, c("fw_id", "productivity", "rho", "env_stoch", "Z", "h")),
  tar_target(pre_sim_files_no_ts, list.files(paste0(sim_dir, "without_cvsp/"))),
  tar_target(sim_iteration_no_ts,
    as.numeric(str_extract(pre_sim_files_no_ts, "simCSh_(\\d+)_", group = 1))
    ),
  tar_target(sim_files_no_ts2, pre_sim_files_no_ts[order(sim_iteration_no_ts)]),
  tar_target(pre_sim_files_ts,
    list.files(sim_dir) %>% #
      .[str_detect(., "_ts")]
    ),
  tar_target(sim_iteration_ts,
    as.numeric(str_extract(pre_sim_files_ts, "simCSh_(\\d+)_", group = 1))
    ),
  tar_target(sim_files_ts2, pre_sim_files_ts[order(sim_iteration_ts)]),
  tar_target(sim_param,
    open_dataset("~/xStressorsStabBEFW/scripts/param_comb_ct_S_h.arrow",
      format = "arrow") %>%
    collect() %>%
    rename(productivity = K, env_stoch = sigma)
    ),
  tar_target(sim_prep,
        open_dataset(paste0(sim_dir, "without_cvsp/", sim_files_no_ts2),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!is.na(richness)) %>%
        mutate(across(c(int_strength, max_int),
            ~map2(.x, S,
              function(y, rich) {
                matrix(y, nrow = rich)
              }
            )
          )
          ) %>%
        # Get matrix of alive species
        mutate(max_int_alive  = map2(max_int, bm_sp,
            function(mat, bm) {
              mask <- bm > 10^-6
              mat[mask, mask, drop = FALSE]
            }
          )
        ) %>%
        select(-max_int),
        pattern = sim_files_no_ts2
      ),
  tar_target(sim_net,
    sim_prep %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int_alive,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        max_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
          ),
        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
        inv_sd_max_int_alive = 1 / sd_max_int_alive,
        gini_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
        avg_omnivory = map_dbl(omnivory, mean),
        disconnected_prod = map_lgl(max_int_alive,
          ~any(colSums(.x) == 0 & rowSums(.x) == 0))
        ) %>%
    select(!where(is.list))
  ),
  tar_target(sim_ts2_null,
    open_dataset(paste0(sim_dir, sim_files_ts2),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        mutate(is_null = map_lgl(species, is.null)) %>%
        select(is_null),
        pattern = sim_files_ts2
        ),
  tar_target(sim_ts_mat,
    open_dataset(paste0(sim_dir, sim_files_ts2), format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          species = map(species, ~matrix(.x, nrow = 100)),
          stoch = map(stoch, ~matrix(.x, nrow = 100))
          ),
    pattern = sim_files_ts2
  ),
  tar_target(sim_ts_mat_param,
    cbind(
      sim_param[!sim_ts2_null$is_null,] %>% select(-A),
      sim_ts_mat
      ) %>%
    as_tibble()
  ),
  tar_target(sim_ts2,
    open_dataset(paste0(sim_dir, sim_files_ts2),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          stoch_d = map2(species, stoch, function(bm, d_stoch) {
            .1 * bm * exp(d_stoch)
            }),
          species = map(species, ~matrix(.x, nrow = 100)),
          stoch = map(stoch, ~matrix(.x, nrow = 100)),
          stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
          cpe = map_dbl(species, compensatory_effect),
          cpe_env = map_dbl(stoch_d, compensatory_effect),
          cpe_int = cpe / cpe_env,
          stab_com = map_dbl(species, community_stability),
          pop_stab = map_dbl(species, population_stability),
          bm_sp = map(species, ~colMeans(.x)),
          bm_total = map_dbl(bm_sp, ~sum(.x)),
          sd_sp = map(species, ~apply(.x, 2, sd)),
          sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
          async = map_dbl(species, asynchrony),
          sae = map(species, statistical_averaging_effect),
          sae_total = map_dbl(sae, ~.x["total"]),
          sae_even = map_dbl(sae, ~.x["even"]),
          evenness_sae = map_dbl(sae, ~.x["eveness"])
        ) %>%
        select(-species, -stoch_d, -stoch),
        pattern = sim_files_ts2
  )
  )
```

```{targets stab_consumer, tar_simple = TRUE}
sim_prep %>% 
  select(all_of(c(var_param_sim, "alive_species", "tlvl", "max_tlvl"))) %>%
  left_join(sim_ts_mat_param) %>%
  filter(!is.na(S), max_tlvl > 1) %>%
  mutate(
    met_loss = map2(Z, tlvl, ~compute_metabolic_loss(Z = .x, tlvl = .y, ax = .88, bx = -0.25)),
    met_loss = map2(met_loss, tlvl, ~.x[.y > 1]),
    species = map2(species, alive_species, ~.x[, .y, drop = FALSE]),
    species = map2(species, tlvl, ~.x[, .y > 1, drop = FALSE]),
    stoch = map2(stoch, alive_species, ~.x[, .y, drop = FALSE]),
    stoch = map2(stoch, tlvl, ~.x[, .y > 1, drop = FALSE]),
    stoch_d = pmap(list(bm = species, d_stoch = stoch, m = met_loss), function(bm, d_stoch, m) {
      bm %*% diag(m, nrow = length(m)) * exp(d_stoch)
      }),
    cpe = map_dbl(species, compensatory_effect),
    cpe_env = map_dbl(stoch_d, compensatory_effect),
    cpe_int = cpe / cpe_env,
    stab_com = map_dbl(species, community_stability),
    pop_stab = map_dbl(species, population_stability),
    bm_sp = map(species, ~colMeans(.x)),
    bm_total = map_dbl(bm_sp, ~sum(.x)),
    sd_sp = map(species, ~apply(.x, 2, sd)),
    sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
    async = map_dbl(species, asynchrony),
    sae = map(species, statistical_averaging_effect),
    sae_total = map_dbl(sae, ~.x["total"]),
    sae_even = map_dbl(sae, ~.x["even"]),
    evenness_sae = map_dbl(sae, ~.x["eveness"])
    ) %>%
  select(-sae, -stoch_d, - max_tlvl)
```

```{targets cons-stab-data}
list(
  tar_target(sim_cons,
    left_join(sim_net %>% select(-async, -stab_com), stab_consumer,
      by = c(var_param_sim, "S"))
    ),
  tar_target(sim_fw_cons,
    sim_cons %>%
      filter(
        max_tlvl > 1,
        sum_sd_sp != Inf,
        bm_total > 10^-5,
        !disconnected_prod
        ) %>%
    select(!where(is.list))
   ),
   tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
   )
```

## Species bm, sd and tlvl

```{targets sim_sp, tar_simple = TRUE, eval = FALSE}
sim_stab_d %>%
  select(all_of(c(var_param_sim, "sd_sp", "bm_sp"))) %>%
  left_join(
    sim_prep_d %>%
      select(all_of(c(var_param_sim_d, "tlvl", "alive_species")))
  ) %>%
  mutate(
    sd_sp = map2(sd_sp, alive_species, ~.x[.y]),
    bm_sp = map2(bm_sp, alive_species, ~.x[.y]),
    cv_sp = map2(sd_sp, bm_sp, ~.x / .y),
    tlvl_bm_sd_sp = pmap(list(tlvl, bm_sp, sd_sp, cv_sp, alive_species),
      function(x, y, z, a, b) {
        rbind.data.frame(list(
        species = b,
            tlvl = x,
            bm_sp = y,
            sd_sp = z,
            cv_sp = a
        )
        )
      }),
    check = map_lgl(tlvl_bm_sd_sp, ~is.null(nrow(.x)))
  ) %>%
  filter(!check) %>%
  select(all_of(c(var_param_sim, "tlvl_bm_sd_sp"))) %>%
  unnest(c(tlvl_bm_sd_sp))
```

## Sim with allometric death 

```{targets prep-allo_sim}
list(
  tar_target(sim_dir_d, '/mnt/parscratch/users/bi1ahd/sim/simCSh_allo_d3/'),
  tar_target(var_param_sim_d, c("fw_id", "productivity", "rho", "env_stoch", "Z", "h")),
  tar_target(sim_files_ts_d,
    list.files(sim_dir_d) %>% #
      .[str_detect(., "_ts")]
    ),
  tar_target(sim_files_no_ts_d,
    list.files(sim_dir_d)%>%
      .[!str_detect(., "_ts")]
    ),
  tar_target(sim_param_d2,
    open_dataset("~/xStressorsStabBEFW/scripts/param_comb_ct_S_h_d_allometric.arrow",
      format = "arrow") %>%
    collect() %>%
    rename(productivity = K, env_stoch = sigma)),
  tar_target(sim_prep_d,
    open_dataset(paste0(sim_dir_d, sim_files_no_ts_d),
      format = "arrow") %>%
    collect() %>%
    # Transform back interaction strength into matrices
    mutate(across(where(is.list), as.list)) %>%
    filter(!is.na(richness)) %>%
    mutate(across(c(int_strength, max_int),
        ~map2(.x, alive_species,
          function(y, sp) {
            mat <- matrix(y, nrow = sqrt(length(y)))
            mat[sp, sp, drop = FALSE]
          }
        )
      )
      ) %>%
  # Per capita interaction strength 
    mutate(across(c(int_strength, max_int),
        ~map2(.x, bm_sp,
          function(y, sp) {
            if (length(sp) > 1) {
              y %*% diag(1 / sp)
            } else {
              y %*% (1 / sp)
            }
          }
        )
      )
      ),
  pattern = sim_files_no_ts_d
  ),
  tar_target(sim_ts_mat_d,
  try({
    open_dataset(paste0(sim_dir_d, sim_files_ts_d), format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          species = map(species,
          ~matrix(.x, nrow = 500)
          ),
          stoch = map(stoch,
          ~matrix(.x, nrow = 500)
          )
          )
          }),
    pattern = sim_files_ts_d
  ),
  tar_target(sim_net_d,
    sim_prep_d %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        max_max_int = map_dbl(max_int,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_int_per_cap =  map_dbl(int_strength,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        avg_max_int = map_dbl(max_int,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int = map_dbl(max_int,
          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
          ),
        cv_max_int = sd_max_int / avg_max_int,
        inv_sd_max_int = 1 / sd_max_int,
        gini_max_int = map_dbl(max_int,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
        avg_omnivory = map_dbl(omnivory, mean),
        disconnected_prod = map_lgl(max_int,
          ~any(colSums(.x) == 0 & rowSums(.x) == 0))
        ) %>%
    select(!where(is.list))
  ),
  tar_target(sim_ts_d,
    try(open_dataset(paste0(sim_dir_d, sim_files_ts_d),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          stoch_d = map2(species, stoch, function(bm, d_stoch) {
            .1 * bm * exp(d_stoch)
            }),
          species = map(species, ~matrix(.x, nrow = 500)),
          stoch = map(stoch, ~matrix(.x, nrow = 500)),
          stoch_d = map(stoch_d, ~matrix(.x, nrow = 500)),
          cpe = map_dbl(species, compensatory_effect),
          cpe_env = map_dbl(stoch_d, compensatory_effect),
          cpe_int = cpe / cpe_env,
          stab_com = map_dbl(species, community_stability),
          pop_stab = map_dbl(species, population_stability),
          bm_sp = map(species, ~colMeans(.x)),
          bm_total = map_dbl(bm_sp, ~sum(.x)),
          sd_sp = map(species, ~apply(.x, 2, sd)),
          sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
          async = map_dbl(species, asynchrony),
          sae = map(species, statistical_averaging_effect),
          sae_total = map_dbl(sae, ~.x["total"]),
          sae_even = map_dbl(sae, ~.x["even"]),
          evenness_sae = map_dbl(sae, ~.x["eveness"])
        ) %>%
        select(-species, -stoch_d, -stoch)),
        pattern = sim_files_ts_d
  )
)
```


# Dataset 

```{targets}
list(
  tar_target(sim_stab_d, sim_ts_d %>% as_tibble()),
  tar_target(sim, left_join(sim_net_d %>%
  select(-async, -stab_com), sim_stab_d, by = "sim_id")),
  tar_target(sim_fw,
    sim %>%
      filter(
        max_tlvl > 1,
        !disconnected_prod
        ) %>%
    select(!where(is.list))
   ),
   tar_target(sim_fw_df, as.data.frame(sim_fw))
  )
```

# SEM

```{targets sem-process}
list(
  tar_target(sim_fw_sem,
    sim_fw_df %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_model_list,
    list(
      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      #richness = lm(richness ~ ct + S, sim_fw_sem),
      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct_alive + richness, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct_alive + richness + h, sim_fw_sem),
      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem, {
    ti <- as.psem(sem_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
      #filter(abs(Std.Estimate) > 0.1)# %>%
#  mutate(
#    Response = var_replacement()[Response],
#    Predictor = var_replacement()[Predictor]
#  ) %>%
    }),
  tar_target(sem_eff, {
    semEff(sem, ci.type = "perc", R = 100, seed = 13, parallel = "snow", data = sim_fw_sem,
      ncpus = future::availableCores() 
    )
    }
  )
)
```


# Make targets  

```{r}
ncpu <- future::availableCores()
if (ncpu > 1) {
  tar_make_future(workers = min(future::availableCores() - 1, 24))
} else {
  tar_make()
}
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.

# Output

```{r load-fun}
sapply(c("targets","tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"), require, character.only = TRUE)  
dir_fun <- "~/xStressorsStabBEFW/"
source(paste0(dir_fun, "R/network_metrics.R"))
source(paste0(dir_fun, "R/string_replacements.R"))
source(paste0(dir_fun, "R/stability_decomposition.R"))
source(paste0(dir_fun, "R/model_helpers.R"))
source(paste0(dir_fun, "R/sem_helpers.R"))
```

```{r}
tar_load(c(sem, sim_fw_sem))


summary(sim_fw$stab_com)
tar_load(sim_prep_d)
tar_load(sim_fw)
tar_load(sim)
tar_load(c(sim_files_ts_d, sim_files_no_ts_d))
tar_load(sim_param_d)
length(sim_files_ts_d) + length(sim_files_no_ts_d)

id_done <- as.integer(str_extract(sim_files_no_ts_d, "_d(\\d+)", group = 1))
id_to_do <- seq(1, 72000, 2000)
(id_to_do[!id_to_do %in% id_done] - 1) / 2000
```

```{r}
tar_load(sim_prep_d)
ti <- sim_prep_d$int_strength[[4265]][sim_prep_d$alive_species[[4265]], sim_prep_d$alive_species[[4265]], drop = FALSE]
mi <- sim_prep_d$bm_sp[[4265]]


m <- matrix(seq(1:9), ncol = 3)
bm <- c(1, 2, .5)
diag(bm)
(map(1:ncol(m), ~m[.x, ] / bm[.x]))

m / matrix(rep(bm, each = nrow(m)), ncol = 3)
rindlist

m / diag(bm)
B
t(apply(m, 1, "/", bm))

summary(sim_fw$avg_omnivory)
```




```{r}
tar_load(sim_prep)
length(sim_prep$tlvl[[1]])
sim_prep$alive_species[[1]]
tar_load(sim_ts_mat_param)
```
```{r}
# Test that matrix multiplication works as expected
x <- 1:3 
y <- matrix(1:6, ncol = 3) 
z <- 1/(y %*% diag(x))
y %*% diag(x)
y %*% diag(x) * z
```

```{r}
tar_load(sim_prep_d)
```



```{r}
tar_load(sim_fw)
sim_fw %>%
  group_by(rho) %>%
  summarise(
    cpe_env = mean(cpe_env, na.rm = TRUE),
    cpe_int = mean(cpe_int, na.rm = TRUE),
    async = mean(async, na.rm = TRUE)
  )
tar_load(stab_consumer)
sim_fw_cons %>%
  group_by(rho) %>%
  summarise(
    cpe_env = mean(cpe_env, na.rm = TRUE),
    cpe_int = mean(cpe_int, na.rm = TRUE),
    async = mean(async, na.rm = TRUE)
  )
object.size(sim_fw_cons) * 10^-6
object.size(sim_fw) * 10^-6
tar_load(sim_fw_cons)
tar_load(sim)
tar_load(sim_files_ts)
tar_load(sim_param)
tar_load(sim_prep)
sim_prep %>%
  filter(max_tlvl > 1) %>%
  group_by(rho) %>%
  summarise(sync = mean(sync, na.rm = TRUE))
colnames(sim_fw)
cor(sim_fw$evenness_sae, sim_fw$rho, use = "pairwise.complete.obs")
```



