---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis
pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html
walks through it in detail. This R Markdown report the example from the chapter.
Try it out in both interactive and non-interactive modes, either by running the
code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above.

```{r, eval = FALSE}
install.packages(c("biglm", "dplyr", "ggplot2", "readr", "targets", "tidyr"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

```{r}
library(targets)
```

Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
dir_fun <- "~/xStressorsStabBEFW/"
source(paste0(dir_fun, "R/network_metrics.R"))
source(paste0(dir_fun, "R/string_replacements.R"))
source(paste0(dir_fun, "R/stability_decomposition.R"))
source(paste0(dir_fun, "R/model_helpers.R"))
```

# Targets

Our first target borrows the `airquality` dataset built into base R.

```{targets raw_sim}
list(
  tar_target(sim_dir, "/mnt/parscratch/users/bi1ahd/sim/simCSh/"),
  tar_target(var_param_sim, c("fw_id", "productivity", "rho", "env_stoch", "Z", "h")),
  tar_target(sim_files_out2, list.files(sim_dir)),
  tar_target(sim_files_no_ts, list.files(paste0(sim_dir, "without_cvsp/"))),
  tar_target(sim_files_ts,
    list.files(sim_dir) %>% #
      .[str_detect(., "_ts")]

    ),
  tar_target(sim_param,
    open_dataset("~/xStressorsStabBEFW/scripts/param_comb_ct_S_h.arrow",
      format = "arrow") %>%
    collect() %>%
    rename(productivity = K, env_stoch = sigma)
    ),
  tar_target(sim_prep,
        open_dataset(paste0(sim_dir, "without_cvsp/", sim_files_no_ts),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!is.na(richness)) %>%
        mutate(across(c(int_strength, max_int),
            ~map2(.x, S,
              function(y, rich) {
                matrix(y, nrow = rich)
              }
            )
          )
          ) %>%
        # Get matrix of alive species
        mutate(max_int_alive  = map2(max_int, bm_sp,
            function(mat, bm) {
              mask <- bm > 10^-6
              mat[mask, mask, drop = FALSE]
            }
          )
        ) %>%
        select(-max_int),
        pattern = sim_files_no_ts
      ),
  tar_target(sim_net,
    sim_prep %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int_alive,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        max_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
          ),
        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
        inv_sd_max_int_alive = 1 / sd_max_int_alive,
        gini_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
        avg_omnivory = map_dbl(omnivory, mean),
        disconnected_prod = map_lgl(max_int_alive,
          ~any(colSums(.x) == 0 & rowSums(.x) == 0))
        ) %>%
    select(!where(is.list))
  ),
  tar_target(sim_ts2_null,
    open_dataset(paste0(sim_dir, sim_files_ts),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        mutate(is_null = map_lgl(species, is.null)) %>%
        select(is_null),
        pattern = sim_files_ts
        ),
  tar_target(sim_ts_mat,
    open_dataset(paste0(sim_dir, sim_files_ts), format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          species = map(species, ~matrix(.x, nrow = 100)),
          stoch = map(stoch, ~matrix(.x, nrow = 100))
          ),
    pattern = sim_files_ts
  ),
  tar_target(sim_ts_mat_param,
    cbind(
      sim_param[!sim_ts2_null$is_null,] %>% select(-A),
      sim_ts_mat
      ) %>%
    as_tibble()
  ),
  tar_target(sim_ts2,
    open_dataset(paste0(sim_dir, sim_files_ts),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          stoch_d = map2(species, stoch, function(bm, d_stoch) {
            .1 * bm * exp(d_stoch)
            }),
          species = map(species, ~matrix(.x, nrow = 100)),
          stoch = map(stoch, ~matrix(.x, nrow = 100)),
          stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
          cpe = map_dbl(species, compensatory_effect),
          cpe_env = map_dbl(stoch_d, compensatory_effect),
          cpe_int = cpe / cpe_env,
          stab_com = map_dbl(species, community_stability),
          pop_stab = map_dbl(species, population_stability),
          bm_sp = map(species, ~colMeans(.x)),
          bm_total = map_dbl(bm_sp, ~sum(.x)),
          sd_sp = map(species, ~apply(.x, 2, sd)),
          sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
          async = map_dbl(species, asynchrony),
          sae = map(species, statistical_averaging_effect),
          sae_total = map_dbl(sae, ~.x["total"]),
          sae_even = map_dbl(sae, ~.x["even"]),
          evenness_sae = map_dbl(sae, ~.x["eveness"])
        ) %>%
        select(-species, -stoch_d, -stoch),
        pattern = sim_files_ts
  ),
  tar_target(sim_stab, cbind(sim_param[!sim_ts2_null$is_null,], sim_ts2) %>% as_tibble()),
  tar_target(sim, left_join(sim_net %>% select(-async, -stab_com), sim_stab, by = c(var_param_sim, "S"))),
  tar_target(sim_fw,
    sim %>%
      filter(
        max_tlvl > 1,
        sum_sd_sp != Inf,
        bm_total > 10^-5,
        !disconnected_prod
        ) %>%
    select(!where(is.list))
   ),
   tar_target(sim_fw_df, as.data.frame(sim_fw))
  )
```

## Species bm, sd and tlvl

```{targets sim_sp, tar_simple = TRUE}
sim_stab %>%
  select(all_of(c(var_param_sim, "sd_sp", "bm_sp"))) %>%
  left_join(
    sim_prep %>%
      select(all_of(c(var_param_sim, "tlvl", "alive_species")))
  ) %>%
  mutate(
    sd_sp = map2(sd_sp, alive_species, ~.x[.y]),
    bm_sp = map2(bm_sp, alive_species, ~.x[.y]),
    cv_sp = map2(sd_sp, bm_sp, ~.x / .y),
    tlvl_bm_sd_sp = pmap(list(tlvl, bm_sp, sd_sp, cv_sp, alive_species),
      function(x, y, z, a, b) {
        rbind.data.frame(list(
        species = b,
            tlvl = x,
            bm_sp = y,
            sd_sp = z,
            cv_sp = a
        )
        )
      }),
    check = map_lgl(tlvl_bm_sd_sp, ~is.null(nrow(.x)))
  ) %>%
  filter(!check) %>%
  select(all_of(c(var_param_sim, "tlvl_bm_sd_sp"))) %>%
  unnest(c(tlvl_bm_sd_sp))
```

```{r}
ncpu <- future::availableCores()
if (ncpu > 1) {
  tar_make_future(workers = min(future::availableCores() - 1, 24))
} else {
  tar_make()
}
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.

# Output

```{r load-fun}
sapply(c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"), require, character.only = TRUE)  
dir_fun <- "~/xStressorsStabBEFW/"
source(paste0(dir_fun, "R/network_metrics.R"))
source(paste0(dir_fun, "R/string_replacements.R"))
source(paste0(dir_fun, "R/stability_decomposition.R"))
source(paste0(dir_fun, "R/model_helpers.R"))
```


```{r}
tar_load(sim_prep)
length(sim_prep$tlvl[[1]])
sim_prep$alive_species[[1]]
tar_load(sim_ts_mat_param)
```

```{r}
tar_load(var_param_sim)
#tar_load(sim_ts_mat_param)
sim_ts_mat_param <- readRDS(here::here("_targets", "objects", "sim_ts_mat_param"))
object.size(sim_ts_mat_param) * 10^-9
tar_load(sim_prep)
object.size(sim_prep) * 10^-9
ti <- sim_prep %>% 
  select(all_of(c(var_param_sim, "alive_species", "tlvl"))) %>%
  left_join(sim_ts_mat_param) %>%
  mutate(
    species = map2(species, alive_species, ~.x[, .y]),
    species = map2(species, tlvl, ~.x[, .y > 1]),
    stoch = map2(stoch, alive_species, ~.x[, .y]),
    stoch = map2(stoch, tlvl, ~.x[, .y > 1]),
    stoch_d = map2(species, stoch, function(bm, d_stoch) {
      .1 * bm * exp(d_stoch)
      }),
    cpe = map_dbl(species, compensatory_effect),
    cpe_env = map_dbl(stoch_d, compensatory_effect),
    cpe_int = cpe / cpe_env,
    stab_com = map_dbl(species, community_stability),
    pop_stab = map_dbl(species, population_stability),
    bm_sp = map(species, ~colMeans(.x)),
    bm_total = map_dbl(bm_sp, ~sum(.x)),
    sd_sp = map(species, ~apply(.x, 2, sd)),
    sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
    async = map_dbl(species, asynchrony),
    sae = map(species, statistical_averaging_effect),
    sae_total = map_dbl(sae, ~.x["total"]),
    sae_even = map_dbl(sae, ~.x["even"]),
    evenness_sae = map_dbl(sae, ~.x["eveness"])
    ) %>%
  select(-sae, -stoch_d)
object.size(ti) * 10^-9
tail(ti$species[[1]])
tail(ti$tlvl[[1]])

tar_load(c(sim_dir, sim_files_ts))
tu <- sim_prep[1:4000,] 
ti <- open_dataset(paste0(sim_dir, sim_files_ts[1]), format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          stoch_d = map2(species, stoch, function(bm, d_stoch) {
            .1 * bm * exp(d_stoch)
            }),
          species = map(species, ~matrix(.x, nrow = 100)),
          stoch = map(stoch, ~matrix(.x, nrow = 100)),
          stoch_d = map(stoch_d, ~matrix(.x, nrow = 100))
          )
```

```{r}
as.vector(ti$species[[1]])
```



