---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis
pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html
walks through it in detail. This R Markdown report the example from the chapter.
Try it out in both interactive and non-interactive modes, either by running the
code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above.

```{r, eval = FALSE}
install.packages(c("biglm", "dplyr", "ggplot2", "readr", "targets", "tidyr"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.


Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
library(tarchetypes)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_config_set(store = "/mnt/parscratch/users/bi1ahd/pre_process_xStressorsStabBEFW_targets/")
tar_option_set(
  memory = "transient", garbage_collection = TRUE,
  error = "null",
  packages = c("tarchetypes", "tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra")
  )
dir_fun <- "~/xStressorsStabBEFW/"
source(paste0(dir_fun, "R/network_metrics.R"))
source(paste0(dir_fun, "R/string_replacements.R"))
source(paste0(dir_fun, "R/stability_decomposition.R"))
source(paste0(dir_fun, "R/model_helpers.R"))
source(paste0(dir_fun, "R/sem_helpers.R"))
compute_metabolic_loss <- function(Z = NULL, tlvl = NULL, ax = .88, bx = -0.25) {
  M = Z ^ (tlvl - 1)
  x = ax*M^(bx)
  x[tlvl == 1] <- 0
  x
}
source(here::here("R", "data_prep.R"))
source(here::here("R", "model_helpers.R"))
```

# Targets





## Sim with allometric death

```{r, eval=FALSE}
#https://books.ropensci.org/targets/static.html#dynamic-within-static-branching 
random_seed_target <- tar_target(random_seed, seq_len(10))
targets <- tar_map(
  values = tibble(method_function = rlang::syms(c("method1", "method2"))),
  tar_target(
    analysis,
    method_function("NIH", seed = random_seed),
    pattern = map(random_seed)
  ),
  tar_target(
    summary,
    summarize_analysis(analysis),
    pattern = map(analysis)
  )
)
tar_delete(starts_with("file_no_ts"))
tar_delete(starts_with("file_ts"))
tar_delete(starts_with("sim_prep"))
tar_delete(starts_with("sim_ts_mat"))
tar_delete(starts_with("sim_ts_prep"))
tar_delete(starts_with("sim_net"))
tar_delete(starts_with("sim_stab"))
tar_delete(starts_with("sim_fw"))
tar_delete(starts_with("sim"))
tar_invalidate(starts_with("file_ts_"))

get_no_ts_file()
tar_load(file_no_ts_no_rerun)
file.exists(file_no_ts_no_rerun)
tar_load(file_ts_no_rerun)
file.exists(file_ts_no_rerun)

library(targets)
tar_load_globals()
tar_load(c(file_ts_non_allo_no_rerun, extinction_threshold))
make_ts_vector_to_matrices(file = file_ts_non_allo_no_rerun,
  ntimestep = 500 
  )

ti <- map_dfr(file_no_ts_no_rerun, ~prep_sim_for_analysis(
      file = .x,
      extinct_bm_threshold = extinction_threshold,
      param_var = var_param_sim_d,
      param_table = sim_param_d2
      ))
length(unique(ti$sim_id))
targets::tar_make(callr_function = NULL)
```

```{targets}
library(tarchetypes)
tar_map(
  values = tibble::tibble(
    dir_name = c("simCSh_allo_d6/", "simCSh_allo_d6_no_rerun/",
      "simCSh_non_allo_d6_no_rerun/", "simCSh_allo_d6_no_rerun_long/", 
      "simCSh_allo_d6_no_rerun_no_disconnected/"),
    name = c("rerun", "no_rerun", "non_allo_no_rerun", "no_rerun_long",
    "no_rerun_no_disconnected"),
    full_path = paste0("/mnt/parscratch/users/bi1ahd/sim/", dir_name)
    ),
  names = "name",
  tar_target(file_no_ts, get_no_ts_file(dir = full_path)),
  tar_target(file_ts, get_ts_file(dir = full_path)),
  tar_target(sim_prep, prep_sim_for_analysis(
      file = file_no_ts,
      extinct_bm_threshold = extinction_threshold,
      param_var = var_param_sim_d,
      param_table = sim_param_d2
      )),
  tar_target(sim_ts_mat,
    make_ts_vector_to_matrices(
      file = file_ts,
      ntimestep = 500),
      pattern = map(file_ts) 

      ),
  tar_target(sim_net, compute_network_metrics(sim = sim_prep)),
  tar_target(sim_ts_prep,
    filter_alive_species_ts_matrices(
      ts_mat = sim_ts_mat,
      prep_sim = sim_prep
    ),
    pattern = map(sim_ts_mat)
  ),
  tar_target(sim_stab,
    compute_stability_metrics_ts(sim_ts_prep = sim_ts_prep),
     pattern = map(sim_ts_prep)
  ),
  tar_target(sim, get_sim_dataset(
      sim_stab = sim_stab,
      sim_net = sim_net
    )),
  tar_target(sim_fw, filter_sim_fw(x = sim)),
  tar_target(sim_fw_sem, get_sem_dataset(x = sim_fw)),
  tar_target(sem_simplified_model_list,
    get_sem_simplified_model_list(sim_fw_sem = sim_fw_sem)),
  tar_target(sem_simplified, get_sem(model_list = sem_simplified_model_list) ),
  tar_target(sem_simplified_coeff, get_sem_coeff(sem = sem_simplified)),
  tar_target(sem_simplified_eff, 
    get_sem_tot_effect(
      sem = sem_simplified,
      sem_data = sim_fw_sem,
      bootstrap_nb = 10,
      nb_cores = min(future::availableCores(), 2),
      ci_type = "perc"
    )
  ),
  tar_target(sem_simplified_collinearity,
  map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
    performance::check_collinearity,
    .id = "response") %>%
  as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(
      Response = var_replacement()[Response],
      R.squared = round(R.squared, 2)
      ) %>%
      select(Response, R.squared)
    )
)
```
```{r, eval = FALSE}
tar_load(c(sim_fw_no_rerun, sim_fw_rerun, sim_non_allo_no_rerun))
tar_manifest() %>%
  filter(str_detect(name, "sim_ts_prep_no_rerun"))
```


```{targets sem, eval = FALSE}
library(tarchetypes)
tar_map(
  values = sim_to_map,
  names = "name",
  tar_target(sem_model_list,
    get_sem_model_list(sim_fw_sem = sim_fw_sem)
    ),
  tar_target(sem, get_sem(model_list = sem_model_list)),
  tar_target(sem_coeff, get_sem_coeff(sem = sem)) #,
#  tar_target(sem_eff,
#    get_sem_tot_effect(
#      sem = sem,
#      sem_data = sim_fw_sem, 
#      bootstrap_nb = 10,
#      nb_cores = future::availableCores(),
#      ci_type = "perc"
#    )
#  )
)
```


```{targets prep-allo_sim}
list(
  tar_target(extinction_threshold, 0),
  tar_target(sim_dir_d, '/mnt/parscratch/users/bi1ahd/sim/simCSh_allo_d5/'),
  tar_target(var_param_sim_d, c("fw_id", "rho", "env_stoch", "Z", "h")),
  tar_target(sim_files_ts_d, get_ts_file(dir = sim_dir_d)),
  tar_target(sim_files_no_ts_d, get_no_ts_file(dir = sim_dir_d)),
  tar_target(sim_param_d2,
    prep_param_table(file = "~/xStressorsStabBEFW/scripts/param_comb_ct_S_h_d3.arrow")
    )
)
```

```{targets sim_for_plot}
list(
  tar_target(sim_prep_for_plot,
  sim_fw %>%
    filter(
      rho %in% c(0, .25, .75, 1),
      h %in% c(1, 2),
      env_stoch %in% c(.1, .3, .6),
      S %in% c(10, 20, 30, 40),
      Z %in% c(1, 10, 100)
      ) %>%
      select(sim_id) %>%
      left_join(sim_prep_d %>%
        select(sim_id, int_strength, tlvl)
      )
    ),
  tar_target(sim_for_plot,
   sim_ts_d_prep %>%
     filter(sim_id %in% sim_prep_for_plot$sim_id) %>%
     left_join(sim_prep_for_plot)
    )
  )
```


# Make targets

```{r force-rerun, eval=FALSE}
#tar_invalidate(names = c(sim_dir_d,sim_files_ts_d,sim_files_no_ts_d,sim_prep_d, sim_ts_mat_d))
#tar_invalidate(names = c(sim_param_d2))
```

```{r tar_make}
i = 1
outdated_obj <- c(1) 
while (i < 10 | length(outdated_obj) > 0) {
  try(tar_make(garbage_collection = TRUE))
  i = i + 1
  outdated_obj <- tar_outdated()
}
```

```{r tar_make_old, eval = FALSE}
ncpu <- future::availableCores()
if (ncpu > 1) {
  tar_make_future(workers = min(future::availableCores() - 1, 24))
  tar_make_future(workers = 5)
} else {
  tar_make()
}
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.

# Output

```{r load-fun}
sapply(c("targets","tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"), require, character.only = TRUE)
dir_fun <- "~/xStressorsStabBEFW/"
source(paste0(dir_fun, "R/network_metrics.R"))
source(paste0(dir_fun, "R/string_replacements.R"))
source(paste0(dir_fun, "R/stability_decomposition.R"))
source(paste0(dir_fun, "R/model_helpers.R"))
source(paste0(dir_fun, "R/sem_helpers.R"))
source(here::here("R", "data_prep.R"))
source(here::here("R", "model_helpers.R"))
```
```{r, eval=FALSE}
```

```{r, eval = FALSE}
tar_load(starts_with("sem_simplified_coeff_"))
ti <- tibble(
    name = c("rerun", "no_rerun", "non_allo_no_rerun", "no_rerun_long",
      "no_rerun_no_disconnected"),
    data = list(
      sem_simplified_coeff_rerun,
      sem_simplified_coeff_no_rerun,
      sem_simplified_coeff_non_allo_no_rerun,
      sem_simplified_coeff_no_rerun_long,
      sem_simplified_coeff_no_rerun_no_disconnected
    )
)

ti %>%
  unnest(data) %>%
  filter(Predictor %in% c("w_avg_tlvl", "ct_alive", "avg_int_strength", "richness")) %>%
  arrange(Response, Predictor) %>%
  print(n = 100)
tar_load(sem_simplified_coeff_no_rerun_no_disconnected)
tar_load(sem_simplified_coeff_no_rerun)

tar_load(sem_simplified_no_rerun_no_disconnected)
tar_load(sem_simplified_no_rerun)
tar_load(sim_fw_sem_no_rerun_no_disconnected)
tar_load(sem_simplified_eff_no_rerun_no_disconnected)
tar_load(sem_simplified_eff_no_rerun)
summary(sem_simplified_eff_no_rerun_no_disconnected)
summary(sem_simplified_no_rerun_no_disconnected)
summary(sem_simplified_no_rerun)
```


```{r, eval = FALSE}
tar_load(sim_fw)
map(c("rho", "h", "env_stoch", "S", "Z"), ~unique(sim_fw[[.x]]))
sim_prep_d %>%
  mutate(omega_alive = map2(omega, alive_species, ~.x[.y, .y, drop = FALSE]))
  select(omega)
sim_prep_d$omega[[1]][sim_prep_d$alive_species[[1]], sim_prep_d$alive_species[[1]]]

sim_fw %>%
  filter(
    rho %in% c(0, .25, .75, 1),
    h %in% c(2, 3),
    env_stoch %in% c(.1, .2, .3, .6),
    S %in% c(10, 30, 40),
    Z %in% c(1, 5, 10, 100)
  )
```

```{r check-failed-sim, eval=FALSE}
tar_load(c(sim_prep_d, sim_param_d2))
sim_param_missing <- sim_param_d2 %>%
  filter(!sim_id %in% sim_prep_d$sim_id)
sim_param_missing %>%
  filter(S == 20)
sim_param_missing %>%
  select(!where(is.list)) %>%
  summary
tar_load(sim)
sim %>%
  filter(max_tlvl <= 1) %>%
  select(!where(is.list)) %>%
  summary()
sim %>%
  filter(disconnected_prod) %>% 
  select(stab_com, everything())

sim %>%
  filter(!disconnected_prod) %>% 
  select(stab_com, everything())
```

```{r, eval=FALSE}
tar_load(c(sem, sim_fw_sem))
tar_load(sem_simplified_eff)

summary(sim_fw$stab_com)
tar_load(sim_prep_d)
tar_load(sim)
sim %>%
  filter(!disconnected_prod)
sim %>%
  filter(max_tlvl <= 1)
sim[sim$sim_id == 3, ]$

tar_load(sim_fw)
tar_load(sim)
tar_load(c(sim_files_ts_d, sim_files_no_ts_d))
tar_load(sim_param_d)
length(sim_files_ts_d) + length(sim_files_no_ts_d)

id_done <- as.integer(str_extract(sim_files_no_ts_d, "_d(\\d+)", group = 1))
id_to_do <- seq(1, 72000, 2000)
(id_to_do[!id_to_do %in% id_done] - 1) / 2000
```

```{r, eval = FALSE}
tar_load(sim_prep_d)
ti <- sim_prep_d$int_strength[[4265]][sim_prep_d$alive_species[[4265]], sim_prep_d$alive_species[[4265]], drop = FALSE]
mi <- sim_prep_d$bm_sp[[4265]]


bm <- c(1, 2, .5)
diag(bm)
(map(1:ncol(m), ~m[.x, ] / bm[.x]))

m / matrix(rep(bm, each = nrow(m)), ncol = 3)
rindlist

m / diag(bm)
bm
t(apply(m, 1, "/", bm))

summary(sim_fw$avg_omnivory)

get_mortality_biomass_dyn <- function(bm, stoch, d) {
  stopifnot(all.equal(length(d), ncol(stoch), ncol(bm)))
  stopifnot(all(is.matrix(bm), is.matrix(stoch)))
  bm %*% diag(d, nrow = length(d)) * exp(stoch)
}

m <- matrix(seq(1:9), ncol = 3)
bm <- c(.1, 1, 10)
stoch <- matrix(rep(1/bm, each = nrow(m)), ncol = 3)

get_mortality_biomass_dyn(bm = bm, stoch = stoch, m = m)
```




```{r}
tar_load(sim_prep)
length(sim_prep$tlvl[[1]])
sim_prep$alive_species[[1]]
tar_load(sim_ts_mat_param)
```
```{r}
# Test that matrix multiplication works as expected
x <- 1:3
y <- matrix(1:6, ncol = 3)
z <- 1/(y %*% diag(x))
y %*% diag(x)
y %*% diag(x) * z
```

```{r}
tar_load(sim_prep_d)
tar_load(sim_fw)
summary(sim_fw$avg_int_strength)
```



```{r}
tar_load(sim_fw)
sim_fw %>%
  group_by(Z, resp_div) %>%
  summarise(
    cpe_env = mean(cpe_env, na.rm = TRUE),
    cpe_int = mean(cpe_int, na.rm = TRUE),
    async = mean(async, na.rm = TRUE)
  )
tar_load(stab_consumer)
sim_fw_cons %>%
  group_by(resp_div) %>%
  summarise(
    cpe_env = mean(cpe_env, na.rm = TRUE),
    cpe_int = mean(cpe_int, na.rm = TRUE),
    async = mean(async, na.rm = TRUE)
  )
object.size(sim_fw_cons) * 10^-6
object.size(sim_fw) * 10^-6
tar_load(sim_fw_cons)
tar_load(sim)
tar_load(sim_files_ts)
tar_load(sim_param)
tar_load(sim_prep)
sim_prep %>%
  filter(max_tlvl > 1) %>%
  group_by(resp_div) %>%
  summarise(sync = mean(sync, na.rm = TRUE))
colnames(sim_fw)
cor(sim_fw$evenness_sae, sim_fw$resp_div, use = "pairwise.complete.obs")
```

```{r save-ts-sample}
dir_to_save <- "/mnt/parscratch/users/bi1ahd/pre_process_xStressorsStabBEFW_targets/objects/"
tar_load(sim_for_plot)
length(unique(sim_for_plot$sim_id))
nrow(sim_for_plot)
save(sim_for_plot, file = paste0(dir_to_save, "sim_for_plot"))
```


